Combining information from photometric and spectroscopic data: Don't waste your time in spectral calibration!

### 2014-04-25 tex/ms.tex

Hello World!
This version of the paper was generated
  from a git repository available at \url{http://github.com/bd-j/something/}
  with git hash \texttt{\githash} (\gitdate).

>>>>

\title{Combining information from photometric and spectroscopic data:
  Don't waste your time in spectral calibration!}
\author{BDJ, DRW, DFM, DWH, CC, others}

\begin{abstract}
Hello World!
\end{abstract}

\keywords{
  greetings
  ---
  whole world
}

All the code used in this project is available under an open-source license
  from \url{http://github.com/bd-j/something/}.
This version of the paper was generated
  from a git repository available at \url{http://github.com/bd-j/speccal/}
  with git hash \texttt{\githash} (\gitdate).
